\emph{How well did your team work together?
Was the distribution of work and the communication among team members effective?
Was the communication with the client effective?}

In general, our team worked really well together.
We were aware of the importance of teamwork within the software engineering process.
If someone was stuck, we helped each other out.
That resulted in spontaneous group coding sessions and motivated us to enforce pair programming as a solid part of our development process.

\subsection{Our communication}
One of the most positive aspects of our project work was the communication within our group.
From the beginning on, we had regular meetings every 2-3 days and tried to coordinate our activities.
If there were problems in our development process, it was mostly because we didn't know or think about more effective way to do it.
But if a team member had the knowledge or thought about something, they always communicated it to the team.
Even if someone thought that there was a better way to do someone else's task, it was always shared and none offense taken.
Of course, there were sometimes misunderstanding regarding the concrete execution of tasks, but usually it was clarified at latest in the next Daily.
As a result, we had a constant workflow that rarely stopped - the communication was effective.
In unofficial retrospectives, we also gave us constructive feedback to do better in the next sprint.

\subsection{Distribution of work}
In terms of work distribution, we strongly considered the interests and skills of the team members.
In pair programming, we also made sure that the team complemented each other well.
At the beginning, we distributed all tasks at once in the sprint planning meeting, which led to some of us not being able to complete their tasks due to incorrect time estimation.
To solve this, we changed this process and only distributed the tasks with the highest priority.
The lower priority tasks could be assigned to a person who was already done with their originally assigned task.
This solved the individual pressure  and made the work distribution more effective.

\subsection{Communcation with the client and customer}
Both the communication with the client and the customer went well, too.
The chair was very helpful and provided us with many opportunities for support (HelpDesk, MidSprint Meeting, Teams).
We made use of the offers and got help quickly, especially with technical problems.
This has resulted in us being held up for less time with technical problems.
Also, in the Review meeting the client gave us constructive feedback with suggestions and tips for improvement.
The customer also gave us constructive feedback and communicated what they were expecting from us.
If we had questions to specify requirements, it was mostly quite clear.