We established three goals for the application, corresponding to the perspectives of our three user types Renter, Provider and Operator. These are:

\begin{itemize}
    \item \textbf{Renters’ perspective:}
    \begin{itemize}
        \item \textit{Purpose:} Make the process of renting a camper van easy and fast.
        \item \textit{Advantage:} Customers will experience less frustration, misunderstandings are avoided.
        \item \textit{Measurement:}
        \begin{itemize}
            \item The booking process is twice as fast as when done physically / by hand / by phone.
            \item 95\% of the renters choose the right vehicle.
        \end{itemize}
    \end{itemize}
    \item \textbf{Provider’s perspective:}
    \begin{itemize}
        \item \textit{Purpose:} Reduce the effort and time needed to manage the booking process.
        \item \textit{Advantage:} Cost reduction and productivity increase (less time is needed for managing the booking process, more time is available for other, more important tasks).
        \item \textit{Measurement:} The provider spends 60\% less time managing the booking process.
    \end{itemize}
    \item \textbf{Operators’ perspective:}
    \begin{itemize}
        \item \textit{Purpose:} To provide the operator means to influence search results.
        \item \textit{Advantage:} Operators can give their own vehicles an advantage.
        \item \textit{Measurement:} Operators rent out twice as many of their own vehicles than without influencing the search results.
    \end{itemize}
\end{itemize}
%\clearpage
