\textbf{Sprint 0:}
\begin{itemize}
    \item In sprint 0, we conducted the Blastoff activities, which produced several artifacts including a Use Case Diagram, and held a User Story workshop. Based on these, we devised a rough project plan, which was discarded after feedback from the client in the sprint review meeting. Instead of spreading the User Stories numerically sorted over the coming sprints, the client advised us to choose User Stories which will present something of value to the customer, and prioritize those which require a lot of feedback.
\end{itemize}
\textbf{Sprint 1:}
\begin{itemize}
    \item In sprint 1 we planned to apply the clients feedback on our artifacts and to realize the first functionalities. We created an extensive prototype and began with the implementation of the lifecycle of the offer object, namely creation and updating.
\end{itemize}
\textbf{Sprint 2:}
\begin{itemize}
    \item The vision for sprint 2 was to, after we implemented the basic functionalities of an offer, to take the next step and make it possible to filter/search offers. Another goal was to begin the implementation of the login and registration functionality, so that we could start realizing user roles in the sprints to come.
\end{itemize}
\textbf{Sprint 3:}
\begin{itemize}
    \item The goal for sprint 3 was to continue our intention to start the realization of user roles and their aspects. We planned to implement the handling of bookings from the renters and the providers perspective.
\end{itemize}
\textbf{Sprint 4:}
\begin{itemize}
    \item Aside from having to catch up with tasks left over from sprint 3, sprint 4 was dedicated to user management, namely the ability of providers to exclude renters, and the ability of operators to block, accept or promote/degrade users. Also planned was to increase our efforts to assure software quality through testing code and the prototype.
\end{itemize}
\textbf{Sprint 5:}
\begin{itemize}
    \item Sprint 5, the final sprint, was dedicated to extensive unit and integration testing of the core parts of the application, as well as fixing any open issues, if possible. The teams focus also lay on realizing a good last increment of the application to show the customer in the final presentation.
\end{itemize}